Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_appendix.tex
appendix updated

In our github repository, we provide several python Juoyter Google Colab anotebooks,
as well as previously generated data,  which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}, 
and using the \texttt{WeightWatcher} tool (version 0.2.7), as described in Table~\ref{table:notebooks}.
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.

>>>>

The results of Section~\ref{sxn:all_cv_models} can be regenerated using
using the \texttt{WeightWatcher} tool (version 0.2.7), as described in Table~\ref{table:notebooks};
the reader may regenerate all the \texttt{WeightWatcher} results using the Google Colab notebooks (in \texttt{ww-colab}),
and/or simply reproduce the Tables and Figures using the Jupyter notebooks (in Table~ref{table:notebooks},
and the pre-computed \texttt{WeightWatcher} datasets (in the \texttt{data/osmr} folder).
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.
